\ttitle

### 2016-03-25 Chapters/Pre_Post_SIRS.tex
Remove more figures and tables
- Remove multiple figures
- Combine all postop CRP figures vs preop crp, alb, bil into one figure
- Remove bodycomp vs alb/neut tables

\begin{figure}[p]
	\caption{Relationship between preoperative CRP levels and postoperative inflammatory markers in the first week after pancreaticoduodenectomy.}
	\label{fig:sirs_crp}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_crp_crp}
		\caption{Preop. CRP vs. postop. CRP}
		\label{fig:sirs_crp_crp}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_crp_alb}
		\caption{Preop. CRP vs. postop. Albumin}
		\label{fig:sirs_crp_alb}
	\end{subfigure}

@@

	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_crp_neut}
		\caption{Preop. CRP vs. postop. Neutrophil count}
		\label{fig:sirs_crp_neut}
	\end{subfigure}	
\end{figure}
%==============================================================================

%========================Albumin vs Post-op SIRS============================================

\begin{figure}[p]
	\caption{Relationship between preoperative Albumin levels and postoperative inflammatory markers in the first week after pancreaticoduodenectomy.}
	\label{fig:sirs_alb}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_alb_crp}
		\caption{Preop. Albumin vs. postop. CRP}
		\label{fig:sirs_alb_crp}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_alb_alb}
		\caption{Preop. Albumin vs. postop. Albumin}
		\label{fig:sirs_alb_alb}
	\end{subfigure}

	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_alb_neut}
		\caption{Preop. Albumin vs. postop. Neutrophil count}
		\label{fig:sirs_alb_neut}
	\end{subfigure}	
\end{figure}
%==============================================================================

@@

%========================Bilirubin vs Post-op SIRS============================================

\begin{figure}[p]
	\caption{Relationship between obstructive jaundice and postoperative inflammatory markers in the first week after pancreaticoduodenectomy.}
	\label{fig:sirs_bilirubin}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_bil_crp}
		\caption{Preop. Bilirubin vs. postop. CRP}
		\label{fig:sirs_bil_crp}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_bil_alb}
		\caption{Preop. Bilirubin vs. postop. Albumin}
		\label{fig:sirs_bil_alb}
	\end{subfigure}

	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_bil_neut}
		\caption{Preop. Bilirubin vs. postop. Neutrophil count}
		\label{fig:sirs_bil_neut}
	\end{subfigure}	
\end{figure}
%==============================================================================

%========================AT vs Post-op SIRS============================================

\begin{figure}[p]
	\caption{Relationship between $\dot{V}_{O_2}$AT and postoperative inflammatory markers in the first week after pancreaticoduodenectomy.}
	\label{fig:sirs_at}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_at_crp}
		\caption{Preop. $\dot{V}_{O_2}$AT vs. postop. CRP}
		\label{fig:sirs_at_crp}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_at_alb}
		\caption{Preop. $\dot{V}_{O_2}$AT vs. postop. Albumin}
		\label{fig:sirs_at_alb}
	\end{subfigure}

	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_at_neut}
		\caption{Preop. $\dot{V}_{O_2}$AT vs. postop. Neutrophil count}
		\label{fig:sirs_at_neut}
	\end{subfigure}	
\end{figure}
%==============================================================================

\input{Tables/sirs_bodycomp_crp}
\input{Tables/sirs_bodycomp_alb}
\input{Tables/sirs_bodycomp_neut}

>>>>

\begin{figure}[p]
	\caption{Relationship between preoperative CRP levels and postoperative CRP in the first week after pancreaticoduodenectomy.}
	\label{fig:sirs_crp}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_crp_crp}
		\caption{Preop. CRP vs. postop. CRP}
		\label{fig:sirs_crp_crp}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_alb_crp}
		\caption{Preop. Albumin vs. postop. CRP}
		\label{fig:sirs_crp_alb}
	\end{subfigure}

@@

	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/sirs_bil_crp}
		\caption{Preop. Bilirubin vs. postop. CRP}
		\label{fig:sirs_crp_neut}
	\end{subfigure}	
\end{figure}
%==============================================================================

@@

\input{Tables/sirs_bodycomp_crp}
